---
title: "finHub API"
output:
  html_document:
    df_print: paged
geometry: margin=1cm
date: '`r format(Sys.Date(), "%A, %B %d, %Y")`'
---

```{=html}
<style>
body {
    position: absolute;
    left: 0px;}
</style>
```


```{r setup, include=FALSE}
require("httr");require("data.table");require("dplyr");require("quantmod")
require("DT")
# get API Key
# https://finnhub.io/dashboard
# Reference URLS: (rate limits are currently set to 30/requests per second)
# https://finnhub.io/docs/api/rate-limit

# environment to store apiKey
pw <- new.env()
# insert your API KEY:
assign("apiKey", "cr8n5r1r01qmmifqslsgcr8n5r1r01qmmifqslt0", envir = pw)
```

## Getting Simple Quotes

Reference: <https://finnhub.io/docs/api/quote>

`stk` = stock symbol

`apiKey` = your api key

```{r simpleQuotes, echo=FALSE}

# build wrapper for simple quotes
getQuoteFH = function(stk,apiKey){
  # create url
  url <- paste0("https://finnhub.io/api/v1/quote?symbol=",stk,"&token=",apiKey)
  # get request
  pg <- GET(url)
  # extract content
  qte <- httr::content(pg) %>% suppressWarnings()
  # convert to data frame
  qte <- as.data.frame(do.call(cbind,qte))
  # change column names
  colnames(qte) <- c("curPRC","change","pctChange","high","low","open","prevClose","timeStamp")
  # format timestamp - set to Eastern Time
  qte$timeStamp <- as.POSIXct(qte$timeStamp,origin = "1970-01-01",tz = "America/New_York")
  # add stock symbol as column
  qte$symbol <- stk
  # return data
  qte
}
# test function
OUT = getQuoteFH(stk="TSLA", apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))

```

## Stock Candles (OHLCV)

Reference: <https://finnhub.io/docs/api/stock-candles>

`stk` = stock symbol

`res` = resolution; accepted values: 1, 5, 15, 30, 60, D, W, M

`from` = character date; ex: "2023-01-01"

`to` = character date; ex: "2023-06-30" - defaults to current date

`apiKey` = your api key

```{r candleData, echo=FALSE}

# build wrapper for OHLCV data
getStkCandlesFH = function(stk,res,from,to=Sys.Date(),apiKey){
  # create url
  url <- paste0("https://finnhub.io/api/v1/stock/candle?symbol=",stk,"&resolution=",res,"&from=",
                as.numeric(as.POSIXct(from)),"&to=",as.numeric(as.POSIXct(to)),"&token=", apiKey)
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  # convert to data frame
  df <- as.data.frame(do.call(cbind, df))
  # re-order columns
  df <- df[,c("t","o","h","l","c","v")]
  # change column names
  colnames(df) <- c("timeStamp","open","high","low","close","volume")
  # change column class
  df$timeStamp <- sapply(df$timeStamp, as.numeric)
  df$open      <- sapply(df$open, as.numeric)
  df$high      <- sapply(df$high, as.numeric)
  df$low       <- sapply(df$low, as.numeric)
  df$close     <- sapply(df$close, as.numeric)
  df$volume    <- sapply(df$volume, as.numeric)
  # format timestamp - set to Eastern Time
  df$timeStamp <- as.POSIXct(df$timeStamp,origin = "1970-01-01",tz = "America/New_York")
  # add stock symbol as column
  df$symbol <- stk
  # return data
  df
}

out <- getStkCandlesFH(stk=ticker, res=1, from=from, to = to, apiKey = pw$apiKey)

# test function
OUT = getStkCandlesFH(stk="SPY", res=1, from="2023-01-01", to = Sys.Date(), apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))

```


## Crypto Candles (OHLCV)

Reference: <https://finnhub.io/docs/api/crypto-candles>

`crypto` = crypto symbol

`res` = resolution; accepted values: 1, 5, 15, 30, 60, D, W, M

`from` = character date; ex: "2023-01-01"

`to` = character date; ex: "2023-06-30" - defaults to current date

`apiKey` = your api key

```{r cryptoCandleData, echo=FALSE}

# build wrapper for crypto OHLCV data
getCryptoCandlesFH = function(crypto,res,from,to=Sys.Date(),apiKey){
  # create url
  url <- paste0("https://finnhub.io/api/v1/crypto/candle?symbol=BINANCE:",crypto,"&resolution=",res,"&from=",
                as.numeric(as.POSIXct(from)),"&to=",as.numeric(as.POSIXct(to)),"&token=",apiKey)
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  # convert to data frame
  df <- as.data.frame(do.call(cbind,df))
  # re-order columns
  df <- df[,c("t","o","h","l","c","v")]
  # change column names
  colnames(df) <- c("timeStamp","open","high","low","close","volume")
  # change column class
  df$timeStamp <- sapply(df$timeStamp, as.numeric)
  df$open      <- sapply(df$open, as.numeric)
  df$high      <- sapply(df$high, as.numeric)
  df$low       <- sapply(df$low, as.numeric)
  df$close     <- sapply(df$close, as.numeric)
  df$volume    <- sapply(df$volume, as.numeric)
  # format timestamp - set to Eastern Time
  df$timeStamp <- as.POSIXct(df$timeStamp,origin = "1970-01-01",tz = "America/New_York")
  # add crypto symbol as column
  df$symbol <- crypto
  # return data
  df
}
# test function
OUT = getCryptoCandlesFH(crypto="ETHUSDT",res='D', from="2023-01-01", to = Sys.Date(), apiKey = pw$apiKey)
# chart candle data
chartSeries(xts(OUT[,c(2:6)], order.by = as.Date(OUT$timeStamp,tz = "America/New_York")),name = OUT$symbol[1])

# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```

## Social Sentiment For Stocks From Reddit/Twitter

Reference: <https://finnhub.io/docs/api/social-sentiment>

`stk` = stock symbol

`apiKey` = your api key

`from` = [OPTIONAL] character date; ex: "2023-01-01"

`to` = [OPTIONAL] character date; ex: "2023-06-30" 

```{r socialSent, echo=FALSE}

# build wrapper for social sentiment - reddit/twitter
getSocialSentFH = function(stk,apiKey,from=NULL,to=NULL){
  # create url
  if(is.null(from) & is.null(to)){
  url <- paste0("https://finnhub.io/api/v1/stock/social-sentiment?symbol=",stk,"&token=",apiKey)
  }else{
    url <- paste0("https://finnhub.io/api/v1/stock/social-sentiment?symbol=",stk,"&from=",
                as.numeric(as.POSIXct(from)),"&to=",as.numeric(as.POSIXct(to)),"&token=",apiKey)
  }
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  if(length(df$reddit) > 0){
    # convert to data frame
    reddit <- as.data.frame(do.call(rbind,df$reddit))
    reddit$source <- "reddit"
    reddit$symbol <-  stk
  }else{
    reddit <- NULL
  }
  if(length(df$twitter) > 0){
    # convert to data frame
    twitter <- as.data.frame(do.call(rbind,df$twitter))
    twitter$source <- "twitter"
    twitter$symbol <-  stk
  }else{
    twitter <- NULL
  }
  # row bind results
  res = rbind(reddit,twitter)
  # return data
  res
}
# test function
OUT = getSocialSentFH(stk="TSLA", apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```


## Earnings Calendar

Reference: <https://finnhub.io/docs/api/earnings-calendar>

`from` = [OPTIONAL] character date; ex: "2023-01-01"

`to` = [OPTIONAL] character date; ex: "2023-06-30" 

`stk` = [OPTIONAL] stock symbol

`international` = [OPTIONAL] Set to true to include international markets. Default value is false

`apiKey` = your api key

```{r earningsCal, echo=FALSE}

# build wrapper for Earnings Calendar
getEarningsCalFH = function(apiKey,from=NULL,to=NULL,stk=NULL,international=NULL){
  # create url
  if(is.null(from) & is.null(to) & is.null(stk) & is.null(international)){
  url <- paste0("https://finnhub.io/api/v1/calendar/earnings?&token=",apiKey)
  }else{
    url <- paste0("https://finnhub.io/api/v1/calendar/earnings?symbol=",stk,"&from=",
                as.numeric(as.POSIXct(from)),"&to=",as.numeric(as.POSIXct(to)),"&international=",
                international,"&token=",apiKey)
  }
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  # row bind results
  res = as.data.frame(rbindlist(df$earningsCalendar,use.names = TRUE, fill = TRUE)) %>% suppressWarnings()
  # return data
  res
}
# test function
OUT = getEarningsCalFH(apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```


## Earnings Surprises

Reference: <https://finnhub.io/docs/api/company-earnings>

`from` = [OPTIONAL] character date; ex: "2023-01-01"

`to` = [OPTIONAL] character date; ex: "2023-06-30" 

`stk` = [OPTIONAL] stock symbol

`international` = [OPTIONAL] Set to true to include international markets. Default value is false

`apiKey` = your api key

Free Tier: Last 4 quarters
```{r earningsSurprises, echo=FALSE}

# build wrapper for Earnings Surprises
getEarningsSuprisesFH = function(stk,apiKey){
  # create url
  url <- paste0("https://finnhub.io/api/v1/stock/earnings?symbol=",stk,"&token=",apiKey)
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  # row bind results
  res = as.data.frame(rbindlist(df,use.names = TRUE, fill = TRUE)) %>% suppressWarnings()
  # return data
  res
}
# test function
OUT = getEarningsSuprisesFH(stk="AMZN",apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```

## IPO Calendar

Reference: <https://finnhub.io/docs/api/ipo-calendar>

`from` = character date; ex: "2023-01-01"

`to` =  character date; ex: "2023-06-30" 

`apiKey` = your api key

Free Tier: Last 4 quarters
```{r ipoCal, echo=FALSE}

# build wrapper for IPO Calendar
getIPOCalFH = function(from,to,apiKey){
  # create url
  url <- paste0("https://finnhub.io/api/v1//calendar/ipo?from=",from,"&to=",to,"&token=",apiKey)
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  # row bind results
  res = as.data.frame(rbindlist(df$ipoCalendar,use.names = TRUE, fill = TRUE)) %>% suppressWarnings()
  # return data
  res
}
# test function
OUT = getIPOCalFH(from="2023-01-01",to=Sys.Date()+30,apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```


## Financials As Reported

Reference: <https://finnhub.io/docs/api/financials-reported>

`stk` = [OPTIONAL] stock symbol

`cik` = [OPTIONAL] stock CIK code

`accessNumber` = [OPTIONAL] Access number of a specific report you want to retrieve financials from.

`freq` = [OPTIONAL] Frequency. Can be either annual or quarterly. Default to annual.

`from` = [OPTIONAL] character date; ex: "2023-01-01"

`to` =  [OPTIONAL] character date; ex: "2023-06-30" 

`apiKey` = your api key

Free Tier: Last 4 quarters
```{r finAsReported, echo=FALSE}

# build wrapper for SEC Financials data
getFinancialsFH = function(stk,cik=NULL,accessNumber=NULL,freq,from=NULL,to=NULL,apiKey){
  # create url
  url <- paste0("https://finnhub.io/api/v1/stock/financials-reported?symbol=",stk,"&freq=",freq,"&token=",apiKey)
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  # row bind results
  RES = lapply(as.list(1:length(df$data)), function(ii){
    #cat("\n",ii)
    # current filing
    tmp = df$data[[ii]]
    #  balance sheet
    BS <- as.data.frame(rbindlist(tmp$report$bs, use.names = TRUE, fill = TRUE))
    BS$rep <- "balanceSheet"
    # income statement
    IS <- as.data.frame(rbindlist(tmp$report$ic,use.names = TRUE, fill = TRUE))
    IS$rep <- "incomeStatement"
    # cash flow statement
    CF <- as.data.frame(rbindlist(tmp$report$cf, use.names = TRUE, fill = TRUE))
    CF$rep <- "cashFlowStatement"
    # row bind all reports
    ALL <- as.data.frame(rbind(BS,IS,CF))
    # add report details
    ALL$accNum <- tmp$accessNumber
    ALL$symbol <- tmp$symbol
    ALL$cik <- tmp$cik
    ALL$year <- tmp$year
    ALL$quarter <- tmp$quarter
    ALL$form <- tmp$form
    ALL$startDate <- tmp$startDate
    ALL$endDate <- tmp$endDate
    ALL$filedDate <- tmp$filedDate
    ALL$acceptedDate <- tmp$acceptedDate
    # make sure it is data frame
    as.data.frame(ALL)
  })
  res = as.data.frame(rbindlist(RES,use.names = TRUE, fill = TRUE)) %>% suppressWarnings()
  # return data
  res
}
# test function
OUT = getFinancialsFH(stk="SPCE",freq="quarterly",apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```

## Insider Sentiment

Reference: <https://finnhub.io/docs/api/insider-sentiment>

`stk` = stock symbol

`from` = character date; ex: "2023-01-01"

`to` = character date; ex: "2023-06-30" 

`apiKey` = your api key

The MSPR ranges from -100 for the most negative to 100 for the most positive which can signal price changes in the coming 30-90 days.
```{r insiderSentiment, echo=FALSE}

# build wrapper for Insider Sentiment data
getInsiderSentimentFH = function(stk,from,to,apiKey){
  # create url
  url <- paste0("https://finnhub.io/api/v1/stock/insider-sentiment?symbol=",stk,"&from=",from,"&to=",to,"&token=",apiKey)
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  # row bind results
  res = as.data.frame(rbindlist(df$data,use.names = TRUE, fill = TRUE)) %>% suppressWarnings()
  # return data
  res
}
# test function
OUT = getInsiderSentimentFH(stk="GOOGL",from="2022-12-01",to=Sys.Date()+60,apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```


## Insider Transactions

Reference: <https://finnhub.io/docs/api/insider-transactions>

`stk` = stock symbol

`from` = [OPTIONAL] character date; ex: "2023-01-01"

`to` = [OPTIONAL] character date; ex: "2023-06-30" 

`apiKey` = your api key

Company insider transactions data sourced from Form 3,4,5, SEDI and relevant companies' filings. This endpoint covers US, Canada, Australia, and selected EU companies. Limit to 100 transactions per API call.
```{r insiderTransactions, echo=FALSE}

# build wrapper for Insider Transactions
getInsiderTransactionstFH = function(stk,apiKey,from=NULL,to=NULL){
  # create url
  if(is.null(from) & is.null(to)){
  url <- paste0("https://finnhub.io/api/v1/stock/insider-sentiment?symbol=",stk,"&token=",apiKey)  
  }else{
    url <- paste0("https://finnhub.io/api/v1/stock/insider-transactions?symbol=",stk,"&from=",from,"&to=",to,"&token=",apiKey)
  }
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  # row bind results
  res = as.data.frame(rbindlist(df$data,use.names = TRUE, fill = TRUE)) %>% suppressWarnings()
  # return data
  res
}
# test function
OUT = getInsiderTransactionstFH(stk="AMZN", apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```


## Basic Financials

Reference: <https://finnhub.io/docs/api/company-basic-financials>

`stk` = stock symbol

`metric` = Metric type. Can be 1 of the following values all

`apiKey` = your api key

Get company basic financials such as margin, P/E ratio, 52-week high/low etc.
```{r basicFinancials, echo=FALSE}

# build wrapper for Basic Financials - Fundamental Ratios
getBasicFinancialsFH = function(stk,apiKey,metric){
  # create url
  url <- paste0("https://finnhub.io/api/v1//stock/metric?symbol=",stk,"&metric=",metric,"&token=",apiKey)  
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
  # most recent
  recent_metrics <- as.data.frame(do.call(rbind,df[["metric"]]))
  recent_metrics <- data.frame(period = as.character(Sys.Date()), v=recent_metrics$V1, type=rownames(recent_metrics), series="mostRecent")
  # ***************************************************************************************************************************
  # annual metrics
  annual_names <- names(df$series$annual[lapply(df$series$annual,length)>0])
  # get all annual metric
  annual_metrics = do.call(rbind,lapply(as.list(annual_names), function(x){
    # extract data
    tmp <- as.data.frame(do.call(rbind,df$series$annual[[x]]))
    # assign metric type
    tmp$type = x
    # assign series type
    tmp$series = "annual"
    # return data
    tmp
  })) %>% as.data.frame
  # ***************************************************************************************************************************
  # quarterly metrics
  quart_names <- names(df$series$quarterly[lapply(df$series$quarterly,length)>0])
  # get all quarterly metric
  quart_metrics = do.call(rbind,lapply(as.list(quart_names), function(x){
    # extract data
    tmp <- as.data.frame(do.call(rbind,df$series$quarterly[[x]]))
    # assign metric type
    tmp$type = x
    # assign series type
    tmp$series = "quarterly"
    # return data
    tmp
  })) %>% as.data.frame
  # ***************************************************************************************************************************
  # row bind all
  res <- as.data.frame(rbind(recent_metrics, quart_metrics, annual_metrics))
  # reclass
  res$period <- sapply(res$period, as.character)
  res$v <- sapply(res$v, as.numeric)
  res$type <- sapply(res$type, as.character)
  res$series <- sapply(res$series, as.character)
  # return data
  res
}
# test function
OUT = getBasicFinancialsFH(stk="AMZN", apiKey = pw$apiKey, metric = "all")
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```


## Company News

Reference: <https://finnhub.io/docs/api/company-news>

`stk` = stock symbol

`from` = character date; ex: "2023-01-01"

`to` = character date; ex: "2023-06-30" 

`apiKey` = your api key

Free Tier: 1 year of historical news and new updates
```{r companyNews, echo=FALSE}

# build wrapper for Company News
getCompanyNewsFH = function(stk,from,to,apiKey){
  # create url
  url <- paste0("https://finnhub.io/api/v1/company-news?symbol=",stk,"&from=",from,"&to=",to,"&token=",apiKey)  
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
   # row bind results
  res = as.data.frame(rbindlist(df,use.names = TRUE, fill = TRUE)) %>% suppressWarnings()
  # fix timestamps
  res$datetime <- as.POSIXct(res$datetime,origin="1970-01-01",tz="America/New_York")
  # return data
  res
}
# test function
OUT = getCompanyNewsFH(stk="ORCL", apiKey = pw$apiKey,from="2023-01-01",to=Sys.Date())
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```


## Company Profile 2

Reference: <https://finnhub.io/docs/api/company-profile2>

`stk` = stock symbol

`apiKey` = your api key

```{r companyProfile, echo=FALSE}

# build wrapper for Company Profile
getCompanyProfileFH = function(stk,apiKey){
  # create url
  url <- paste0("https://finnhub.io/api/v1/stock/profile2?symbol=",stk,"&token=",apiKey)  
  # get request
  pg <- GET(url)
  # extract content
  df <- httr::content(pg) %>% suppressWarnings()
   # row bind results
  res = as.data.frame(do.call(cbind,df)) %>% suppressWarnings()
  # return data
  res
}
# test function
OUT = getCompanyProfileFH(stk="META", apiKey = pw$apiKey)
# OUTPUT
DT::datatable(OUT,rownames = FALSE,extensions = "Buttons", options = list(dom="Blfrtip", buttons = c('copy', 'csv', 'excel')))
```